Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-14 paper.tex
minor
Reword k results

The value of $k$ for each \rev{instability mode} is calculated as $k
= 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the
perturbation, measured as the difference between the two peaks closest to $z=0$
(thus minimising the influence of line-tying on the
measurement). \rev{In particular, the two peaks closest to $z=0$ of
  the pressure profile are used to calculate the wavenumber of
  the flute mode $k_{\text{flute}}$ and those of the radial velocity
  profile are used to calculate the wavenumber of
  the kink mode $k_{\text{kink}}$, respectively.} This gives
a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both
viscosity models. Hence, the observed most unstable fluting perturbation is
that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the
observed kink instability is that where $m=1$ and $k=4.57$. Using these values,
it is observed that the fluting perturbation exactly resonates with the field,
that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$
(Figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
of peak linear \rev{flute growth $r_s$} seen in
Figure~\ref{fig:growth_rate_4}. At this time the perturbation is close
to resonance, that is $m B_{\theta}(r)/r + kB_z(r)\approx 0$, over a
range of radii from $r=0.125$ to $0.2$.

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{$\eta=10^{-4}$}& \multicolumn{2}{c}{$\eta=10^{-3}$} \\
&
Anisotropic &
\rev{Isotropic} &
Anisotropic &
\rev{Isotropic} \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\todo{WHY WAS ROW REMOVED?} Observed radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& \rev{23.74}
& \rev{23.52}
& \rev{17.15}
& \rev{17.60}\\
Observed axial wave number $k_{\text{flute}}$
& $22.67 \pm 1$
& \rev{$22.71 \pm 1$}
& $16.12 \pm 0.4$
& \rev{$16.25 \pm 0.4$}\\
Observed axial wave number $k_{\text{kink}}$
& {4.57}
& \rev{4.41}
& {3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& \rev{$1.64 \times 10^{-2}$}
& \rev{1.28}
& \rev{$2.89 \times 10^{-3}$}
& \rev{0.370} \\
\rev{Cumulative Ohmic heat at $t=50$}
& \rev{3.06}
& \rev{2.75} 
& \rev{6.54} 
& \rev{6.27} \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

>>>>

The value of $k$ for each \rev{instability mode} is calculated as $k
= 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the
perturbation, measured as the difference between the two peaks closest to $z=0$
(thus minimising the influence of line-tying on the measurement). This gives
a value of $k_{\text{flute}}=22.93$ and $k_{\text{kink}}=4.57$ for the
anisotropic model and $k_{\text{flute}}=22.30$ and $k_{\text{kink}}=4.41$.
Using these values, it is observed that the fluting perturbation resonates with
the field, that is $m B_{\theta}(r)/r + kB_z(r) \approx 0$, over a range of
$0.15 \lesssim r \lesssim 0.225$ (Figure~\ref{fig:resonant_surface_4}). This is
in close agreement with the predicted radius of peak linear \rev{flute growth
$r_s$} seen in Figure~\ref{fig:growth_rate_4}.

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.}} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{$\eta=10^{-4}$}& \multicolumn{2}{c}{$\eta=10^{-3}$} \\
&
Anisotropic &
\rev{Isotropic} &
Anisotropic &
\rev{Isotropic} \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\todo{WHY WAS ROW REMOVED?} Observed radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& \rev{23.74}
& \rev{23.52}
& \rev{17.15}
& \rev{17.60}\\
Observed axial wave number $k_{\text{flute}}$
& $22.67 \pm 1$
& \rev{$22.71 \pm 1$}
& $16.12 \pm 0.4$
& \rev{$16.25 \pm 0.4$}\\
Observed axial wave number $k_{\text{kink}}$
& {4.57}
& \rev{4.41}
& {3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& \rev{$1.64 \times 10^{-2}$}
& \rev{1.28}
& \rev{$2.89 \times 10^{-3}$}
& \rev{0.370} \\
\rev{Cumulative Ohmic heat at $t=50$}
& \rev{3.06}
& \rev{2.75} 
& \rev{6.54} 
& \rev{6.27} \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}
